\documentclass{scrartcl}
\usepackage{multicol}
\usepackage{url}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{color}
\usepackage[parfill]{parskip}
\usepackage{titlesec}
\usepackage{geometry}

\title{Large-scale drive-by download detection: boot. visit$^n$. kill. repeat.}
\subtitle{Master in System and Network Engineering}
\author{
  Adriaan Dens\\
   \texttt{adriaan.dens@os3.nl}
  \and
  Martijn Bogaard\\
   \texttt{martijn.bogaard@os3.nl}
}

\begin{document}
\maketitle

\tableofcontents

\section{Abstract}

\section{Acknowledgements}

\section{Introduction}
\input{introductie.tex}

\section{Research Question}
\input{rq.tex}

\section{Related work}
\input{rw.tex}

\section{Web browser internals}

Which techniques are used by browsers to make concurrently visiting multiple
URLs possible?
	- Tabs of course
		- As a process
		- As multiple threads under the browser process

How can we link an HTTP request to its source URL without the modification of the used web browser?
we need extra information, see vraag 4
network is niet genoeg blablabla

How do web browsers make HTTP requests and retrieve webpages? Which Operating System level APIs are used?
	- Safari: CFNetwork and NSURLConnection(Loader) and IPC
		1 hoofdprocess: Safari
		1 process per tab: Safari Web Content
		1 process voor networking: Safari Networking
		Network stack of OS X.
	- Internet Explorer: C API calls naar Windows libraries
		Process per tab: is configureerbaar in settings/registry, je kan ook meerdere tabs in 1 process hebben
		Network stack of Windows
	- Firefox: C++ Library calls
		Single Process (+ 1 process voor flash)
		Own network stack Necko (nss3 voor trafiek te encrypten)
		\url{https://developer.mozilla.org/en-US/Firefox/Releases/3.5/Updating_extensions#Getting_a_load_context_from_a_request}
		http://stackoverflow.com/questions/10719606/is-it-possible-to-know-the-target-domwindow-for-an-httprequest
	- Chrome: IPC 
		1 hoofdprocess: Google Chrome die networking doet
		1 process per tab. (Altijd 13 threads?)
		1 process voor Flash.
		1 process voor Audio. (4 threads)
		Own network stack (nss3 voor trafiek te encrypten)
		http://www.chromium.org/developers/design-documents/network-stack

What extra information from the client's (running) machine can be used to augment the information gained from network trac to make the tracking of malware to its source URL easier?  
	- The Thread ID or Process ID van tabs, PDF reader, Java applet, ...
	- Handle bij IE
	- File descriptors
	- Process tree
	- Voordeel van op machine network traffic te intercepten is dat we rommel van andere applicaties niet zien, maar enkel het trafiek van de browser en de gespawnde subprocessen ervan.
	- 

\section{Generic algorithm}

- Disconnected DAGs

1) Hooker schrijven voor elke browser die trafiek tussen Netwerk en Browser of in de browser zelf monitort en doorgeeft aan Cuckoo
2) DAG opstellen door de extra informatie te gebruiken in report.json
3) DAG interpreteren, nodes met enkel uitgaande edges zijn de beginnende URL
4) Kijken of er iets raar gebeurt in elk eiland
5) Reporting

\section{Platform specific problems}

Unix heeft geen handles zoals Windows maar meer files


\section{Proof of Concept}
	- Cuckoo aanpassen
		- Multiple URL support
		- Fixed Yara
	- Analyzer in Python
		- report.json parser
		- Commandline interface
			- Input: file, lijst op cli
			- Generic algorithm
			- Output: "No Malicious activity found", "URL xxxxx shows malicious activity: en dan wat korte informatie" 
		- 

\section{Results}

Speedboost tussen Cuckoo 1.2-dev en onze wijzigingen, grafiekjes maken


\section{Ethical issues}
\input{ei.tex}

\section{Conclusion}


\bibliographystyle{ieeetr}
\bibliography{report}

\end{document}
